Pushdown Control-Flow Analysis via Refunctionalization

### 2018-02-24 paper.tex

Tranditionally, continuation-passing style is a popular intermediate representation
for analyzing functional programs because of it exposes control transfer explicitly
and simplifies the analysis \cite{Shivers:1991:SSC:115865.115884, Shivers:1988:CFA:53990.54007}.
Here, we choose to use a direct-style intermediate representation as target for
clarity but without losing simplicty and generality.
The transformations we will show in the rest of this paper
also work on abstract machines for plain $\lambda$-calculus languages.

>>>>

Tranditionally, continuation-passing style (CPS) is a popular intermediate representation
for analyzing functional programs because of it exposes control transfer explicitly
and simplifies the analysis \cite{Shivers:1991:SSC:115865.115884, Shivers:1988:CFA:53990.54007}.
Here, we choose to use a direct-style intermediate representation as target for
clarity but without losing simplicty and generality.
The transformations we will show in the rest of this paper
also work on abstract machines for plain $\lambda$-calculus languages.
